---
title: "p8105_hw6_ls3751"
author: "Liucheng Shi"
output: github_document

---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r packages}
library(tidyverse)
library(modelr)
library(skimr)
set.seed(7)
```


### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

### Load and clean the data for regression analysis

```{r, message = F}
bw_df = read_csv("./data/birthweight.csv") %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform))
```


```{r}
bw_df %>% 
  skim()
bw_df = bw_df %>% 
  select(-pnumlbw, -pnumsga)
```

There is no missing value in the current dataset. Since data entries for two variables __pnumlbw__ and __pnumsga__ are zero, we choose to drop these variables.

### Regression Model

```{r}
bw_dfm = bw_df %>% 
  select(-parity, -malform, -smoken, -frace, -ppwt, -delwt)
```


Besides variables mentioned above, variables __parity__, __malform__, and __smoken__ are highly skewed, thus I choose to remove the three variables. Variables _ppwt__ and __delwt__ are also removed considering mother's weight at delivery minus mother's weight before pregnancy equals the Variable _wtgain__. Based on the hypothesis that father's race is not significantly associated with brith weight, the predictor variables used in my model are `r names(bw_dfm)`. 

```{r}
bw_model = lm(bwt ~ ., data = bw_dfm)
summary(bw_model)
bw_newmodel = lm(bwt ~ babysex + bhead + blength + fincome + gaweeks + mheight + mrace + ppbmi + wtgain, data = bw_dfm)
```

Since the coefficients of variables __menarche__ and __momage__ are not significant at 0.1 significance level, the R-sqaured is not impaired after dropping the two variables(`r summary(bw_model)$r.squared ` vs. `r summary(bw_newmodel)$r.squared `)

```{r}
bw_newmodel %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable()
```

### Residuals plot

```{r model residuals against fitted values}
bw_dfm %>% 
  add_residuals(bw_newmodel) %>% 
  add_predictions(bw_newmodel) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  stat_smooth(method = "lm")
```



### Cross Validation

```{r}
cv_df = 
  crossv_mc(bw_dfm, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(model_1  = map(train, ~lm(bwt ~ babysex + bhead + blength + fincome + 
                                     gaweeks + mheight + mrace + ppbmi + wtgain, data = .x)),
         model_2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model_3  = map(train, ~lm(bwt ~ blength*bhead*babysex, data = .x))) %>% 
  mutate(rmse_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
         rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))
```

```{r cross validation}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin() +
  labs(
    title = "Comparing RMSE values for Three Linear Models",
    x = "Model",
    y = "RMSE"
  ) 
```

Based on the violin plot, model 1(my model) has the lowest level of prediction error probably due to the the large number of predictor variables. The best model is model 1 (babysex + bhead + blength + fincome + gaweeks + mheight + mrace + ppbmi + wtgain).

## Problem 3

Load the dataset
```{r, cache = T}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Generate 5000 bootstrap samples for distributions of interests

```{r, cache = T}
bootstrap_rsquared <-
  weather_df %>%
  select(tmax, tmin) %>% 
  bootstrap(5000, id = "sample_id") %>% 
  mutate(model = map(.x = strap, ~lm(tmax ~ tmin,data = .x)),
         result = map(model, broom::glance)) %>% 
  select(sample_id, result) %>% 
  unnest(result) 
```

```{r, cache = T}
bootstrap_logbeta <-
  weather_df %>%
  select(tmax, tmin) %>% 
  bootstrap(5000, id = "sample_id") %>% 
  mutate(model = map(.x = strap, ~lm(tmax ~ tmin,data = .x)),
         result = map(model, broom::tidy)) %>% 
  select(sample_id, result) %>%
  unnest(result) %>%
  select(sample_id, term, estimate) %>% 
  mutate(term = str_replace(term, "\\(Intercept\\)", "intercept")) %>% 
  pivot_wider(names_from = term,
              values_from = estimate) %>% 
  mutate(logbeta = log(intercept * tmin))
```

### Plot the distibutions

```{r}
bootstrap_rsquared %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    title = "The distribution of r squared",
    y = "Density"
  )
bootstrap_logbeta %>% 
  ggplot(aes(x = logbeta)) +
  geom_density() +
  labs(
    title = " The distribution of log(beta0*beta1)",
    y = "Density"
  )
```

It is noticeable from the two distribution plots that both estimators are approximately normally distributed.

### 95% Confidence intervals and quantiles

```{r}
bootstrap_rsquared %>% 
  summarize(
    CI_lower = quantile(r.squared, 0.025),
    CI_upper = quantile(r.squared, 0.975)
  )
bootstrap_logbeta %>% 
  summarize(
    CI_lower = quantile(logbeta, 0.025),
    CI_upper = quantile(logbeta, 0.975)
  )
```

